Stage-Splitting a Modal Language

### 2014-10-10 paper/relatedwork.tex
relatedwork

@@

@@

>>>>

\subsection{Umut's notes}

---- DO NOT DELETE ----

Answer the following question for all of the related work:

What happens when we try to write quickselect as a meta program?

\paragraph{Partial Evaluation.}
Online and offline.  Both approaches have their merits but online
partial evaluation can be too slow and if stopped lead to an
inefficient residual.  Offline partial evaluation is faster.  Also,
full self-application has only been achieved by offline partial
evaluation.

Weaknesses of partial evaluation include~\cite{GJ05}:
1) speedups linear in the subject programs run time (excuse moi?)

2) good speedups require close knowledge of the program and some
binding-time improvements.

3) result of specialization can be hard to predict as it can lead to
slowdown, code explosion, and non-termination at specialization time.

\paragraph{Meta programming}

What happens when we try to write quickselect as a meta program?

@@

Is in possible for the residual program to not terminate (unexpectedly)?

@@

Based on Glenstrup and Jones (pp. 1154, 1155), a partial evaluator
should be complete. That is every computation depending on the static
input should be reduced to a value (during specialization).
Unfortunately, completeness is difficult to achieve if we also require
that the specialization is always terminating.

One problem with their description is that it is not clear which
termination problem they are talking about termination of the residual
or the specializer.

Nontermination during specialization: 
consider code

double x = doubleplus (x,0)

doubleplus (u,v) = if u <= 0 then v else doubleplus (u-1,v+2)

this can lead to non-termination if v is considered static.

Is this a problem for us?

\paragraph{Supercompilation.}
~\cite{Turchin86}
